\documentclass[14pt]{extarticle}
\usepackage{extsizes}
\usepackage{HistoryTemplate}

\title{1920s Essay Body Paragraph 1}
\author{Matthew Stringer}
% \date{}
\lhead{Matthew Stringer}
\rhead{Body Paragraph 1}
\cfoot{Honors History}
\rfoot{\thepage}

\begin{document}
    \maketitle
    In the 1920s, the government did little in order to protect African-Americans.
% 
    First, progressive reforms made before the outbreak of the war did not affect 
    African-Americans. By ignoring the African-American populus, the government 
    isolated this group and which lead to further oppression. Also, progressive
    reforms were meant to protect workers' rights, however, the government's 
    intentional ignorance of African-American working condition laid the foundation
    for the further humiliation and oppression of African-Americans.
% 
    Second, African-Americans were robbed of the right to vote.
    Without this, African-Americans were not able to participate in democracy and 
    create change that improved their living condition, and protected them from racist
    laws and leaders.
% 
    Third, African-Americans were offered little education from the government.
    This lack of education caused the public to view African-Americans as unintelligent 
    and their rights were not taken seriously.
% 
    The lack of government protection lead to the hatred of African-Americans and 
    the continuation of traditional oppression.
\end{document}