\documentclass[12pt]{article} %was 12pt
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{graphicx}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{amsthm}
\usepackage{enumitem} % to change appearance of enum and item environments
\usepackage{framed}
\usepackage{color}
\usepackage{multicol}
%Matthew
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
%end Matthew

%\usepackage{yhmath}
% adjust the margins using the geometry package
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage[parfill]{parskip}
 %\usepackage{mathpazo}
%\usepackage{euler}


% customize the headers using the fancyhdr package
\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage{hyperref}

\usepackage{mathrsfs}
\usepackage{mathtools}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\newenvironment{hwproblem}[1]{{\large \bfseries Problem #1\,:} \begin{trivlist}\item[]\vspace{-0.5ex}}{\end{trivlist}\vspace{3ex}}
\newenvironment{hwproblemquestion}[1]{{\bfseries Question #1\,:} \begin{trivlist}\item[]\vspace{-1.5ex}}{\end{trivlist}\vspace{3ex}}


% customize enumerate and itemize environments
\setlist[itemize]{labelsep=1ex,itemsep=1.5ex,parsep=0ex,leftmargin=4ex,topsep=0.5ex}
\setlist[enumerate]{labelsep=1ex,itemsep=1.5ex,parsep=0ex,leftmargin=4ex,topsep=0.5ex}




\rhead{Honors US History}
\lhead{Matthew Stringer} % your name
\lfoot{}
\cfoot{Summer Homework}  % change to the corresponding number
\rfoot{\thepage}

\setlength{\headheight}{15pt} 
\title{Summer Assignment} % change to the corresponding number
\date{September 5, 2018}
\author{Matthew Stringer \\ 60766177} % your name and ID number

% Anything above the \begin{document} is the template. If you wish to start a new document using this template, erase everything inside of the \begin{document}...\end{document}
\allowdisplaybreaks
\setlength{\parindent}{4em}
\begin{document}
\maketitle
\section{Political Issues}
The most important political event of the summer this year was the United States withdrawal from the United 
Nations Human Rights Council. Secretary of Sate Mike Pompeo and U.N. Ambassador Nikki Haley announced 
the decision. Nikki Haley told the media, "I want to make it crystal clear that this is not a retreat 
from human rights commitments. On the contrary, we take this step because our commitment does not
allow us to remain a part of a hypocritical and self-serving organization that makes a mockery of 
human rights." This decision was predictable considering the fact that the Trump administration
has been criticizing the U.N. for several perceived failures. They have complained the loudest about
their "chronic bias against Israel" in particular. 
%my part
I disagree with this decision, when we joined the council in 2009, the Obama administration joined
knowing that problems existed inside of the council. However, they continued to join instead so that
they could "make the council a more effective forum to promote and protect human rights" by making changes
from within. As Representative Eliot Engel said when describing the issues with the human rights council,
"the way to deal with this challenge is to remain engaged and work with partners to push for change." I 
believe that in order to fix the problems that contaminate the Human Rights Council, we must penetrate
it from within and push its members to focus on actual human rights issues and move past debating the
legitimacy of Israel as a nation. 
\subsection*{Notes:}
\begin{itemize}
	\item 2018 North Korea and US summit held in Singapore. First summit between US President and
	North Korean leader. (June 12)
	\item Greece and Republic of Macedonia reach a deal to end a near 27-year old naming dispute
	between both countries. Macedonia is officially renamed the Republic of North Macedonia. (June 12)
	\item \textbf{US announces it will withdraw from the United Nations Human Rights Council. (June 19)}
	\item Canada legalizes cannabis for recreational use. This will take effect October 17. (June 19)
	\item Eritrea and Ethiopia declare and end to their twenty-year conflict. (July 9)
	\item 2018 Brussels NATO summit held in Belgium. (July 11-12)
	\item US reimposes sanctions in Iran. (August 7)
	\item Arizona Senator John McCain passed away at the age of 81 (August 25)
\end{itemize}

\section{Cultural Events}
The most important Cultural Event of the summer was Saudi Arabia allowing women to drive on
July 24, 2018. Leaders decided to in-act this change because they believed that the change would help
the economy. Before, woman had to spend large amounts of money in order to pay for male drivers to
transport them to work. Rights groups in Saudi Arabia have long fought for the ban to revoked. Some
women have been arrested and jailed for driving in protest of the ban. I believe this is the most 
important Cultural Event of the summer because it marks a progressive change in Saudi Arabia. 
Unfortunately, Saudi Arabia is known for its patriarchal laws and sexists policies. Hopefully, this
change will spark a progressive push in Saudi Arabia's society.
\subsection*{Notes:}
\begin{itemize}
	\item More than 109 people are killed by the eruption of Guatemala's deadliest volcano. (June 3)
	\item 2018 FIFA World Cup is held in Russia and won by France. (June 14-15)
	\item Seventeen people die in Caracas, Venezuela after the El Paraiso stampede after a tear gas
	canister is detonated in a crowded club. (June 16)
	\item 2018 Mediterranean Games are held in Tarragona, Spain. (June 22 - July 1)
	\item \textbf{Saudi Arabia allows women to drive. (June 24)}
	\item Aum Shinrikyo leader Shoko Asahara and six other main members who led the 1995 Tokyo subway
	sarin attack are executed by hanging. (July 6)
	\item Scientists report the presence of a subglacial lake on Mars, 1.5 km below the southern polar 
	ice cap (July 25)
\end{itemize}

\section{Economic Conditions}
The most important economic event that happened in the U.S. this summer was Facebook 20\% drop. On 
July 26, Facebook lost about \$120 billion in market capitalization after the market close. This
occurred after it missed expectations on revenue and demonstrated a decrease in the rate of user
growth. Investors undid all of Facebook's 2018 gains during this loss. This event has been the
"ugliest single-session decline since the company went public in 2012." 
%my part
I believe that this event is the most important economic event of the summer because, it demonstrates
Facebook's decline in popularity over recent years. In my own experience, many of friends and 
younger family don't use Facebook and instead opt to use more modern social applications like 
Instagram and Snapchat. The major reason behind using these programs is due to their built in privacy
features. For example, Snapchat automatically removes messages that are sent to individual people
immediately after they are read. Also, Snapchat warns users when someone else decides to take a 
screen shot of a post or message. Along with this, Snapchat is automatically configured so that 
only friends are allowed to view posts to the "story". Because of these many built in privacy features,
both Snapchat and Instagram have been widely used amongst young people today, replacing Facebook.
\subsection*{Notes:}
\begin{itemize}
	\item Lithuania becomes 36th member of OECD. (July 5)
	\item EU-Japan Economic Partnership is signed, which is the world's largest bilateral free trade
	deal, creating an open trade zone covering nearly one-third of global GDP. (July 17)
	\item \textbf{The share price of Facebook drops by almost 20 percent after company warns investors that user growth
	has slowed following the data leak scandal. Over \$109 billion is wiped from its market value. (July 26)}
	\item Apple becomes the world's first public company to achieve a market capitalization of \$1 trillion. (August 2)
\end{itemize}

\end{document}
