\documentclass[12pt]{article} %was 12pt
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{graphicx}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{amsthm}
\usepackage{enumitem} % to change appearance of enum and item environments
\usepackage{framed}
\usepackage{color}
\usepackage{multicol}
%Matthew
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
%end Matthew

%\usepackage{yhmath}
% adjust the margins using the geometry package
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage[parfill]{parskip}
 %\usepackage{mathpazo}
%\usepackage{euler}


% customize the headers using the fancyhdr package
\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage{hyperref}

\usepackage{mathrsfs}
\usepackage{mathtools}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\newenvironment{hwproblem}[1]{{\large \bfseries Problem #1\,:} \begin{trivlist}\item[]\vspace{-0.5ex}}{\end{trivlist}\vspace{3ex}}
\newenvironment{hwproblemquestion}[1]{{\bfseries Question #1\,:} \begin{trivlist}\item[]\vspace{-1.5ex}}{\end{trivlist}\vspace{3ex}}


% customize enumerate and itemize environments
\setlist[itemize]{labelsep=1ex,itemsep=1.5ex,parsep=0ex,leftmargin=4ex,topsep=0.5ex}
\setlist[enumerate]{labelsep=1ex,itemsep=1.5ex,parsep=0ex,leftmargin=4ex,topsep=0.5ex}




\rhead{Honors US History}
\lhead{Matthew Stringer} % your name
\lfoot{}
\cfoot{Notes}  % change to the corresponding number
\rfoot{\thepage}

\setlength{\headheight}{15pt} 
\title{Chapter 15 Notes} % change to the corresponding number
%\date{September 5, 2018}
\author{Matthew Stringer \\ 60766177} % your name and ID number

% Anything above the \begin{document} is the template. If you wish to start a new document using this template, erase everything inside of the \begin{document}...\end{document}
\allowdisplaybreaks
\setlength{\parindent}{4em}
\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Presidential Leadership and Reconstruction}
\subsection{Lincoln's Policies (1863-1865)}
\subsubsection{Proclamation of Amnesty and Reconstruction}
\begin{enumerate}
	%\item Lincoln saw the Confederates as a "disloyal minority" not traitors.
	\item Lincoln set up a process for political reconstruction
	\item Lincoln gave presidential pardons to Confederates that:
	\begin{enumerate}
		\item took an oath of allegiance to the Union
		\item accepted the emancipation of slaves.
	\end{enumerate}
	\item A state could be considered legitimate if at least 10\% of the voters took the loyalty oath.
	\item This required states to rewrite their constitution in order to eliminate slavery.
\end{enumerate}

\subsubsection{Wade-Davis Bill}
\begin{enumerate}
	\item Many Republicans objected to Lincoln's 10\% plan
	\item The Wade-Davis Bill required 50\% of voters to take a loyalty oath and only non-Confederates
		to vote for a new constitution.
	\item Lincoln pocket-vetoed the bill.
\end{enumerate}

\subsubsection{Freedmen's Bureau}
\begin{enumerate}
	\item Congress created a new agency, the Freedmen's Bureau
	\item Acted as an early welfare agency, providing food, shelter, and medical aid for those made
		destitute by the Civil War.
	\item Created 3,000 schools for freed blacks including colleges.
	\item Taught 200,000 African Americans how to read.
\end{enumerate}

\subsubsection{Lincoln's Last Speech}
\begin{enumerate}
	\item Lincoln encouraged Northerners to accept Louisiana as a state.
	\item Lincoln's suggested that he had become more progressive 
	\item Hope for lasting reform was devastated after Lincoln's Assassination.
\end{enumerate}

\subsection{Andrew Johnson and Reconstruction (1865-1868)}
\begin{enumerate}
	\item Johnson was the only Confederate from Tennessee that was loyal to the Union
	\item Republicans picked him to Lincoln's running mate in 1864 in order to encourage pro-Union
		to vote for the Republican Party.
	\item Johnson became the wrong person for the job due to his white supremacy and was bound to 
		clash with Republicans in Congress.
\end{enumerate}

\subsubsection{Johnson's Reconstruction Policy}
\begin{enumerate}
	\item Johnson issued his own Reconstruction proclamation that was similar to Lincoln's 10\% plan.
	\item It provided for the disfranchisement (loss of the right to vote and hold office) of 
	\begin{enumerate}
		\item All former leaders and officeholders of the Confederacy
		\item Confederates with more than \$20,000 in taxable property.
	\end{enumerate}
	\item Johnson still retained the power to pardon to "disloyal" Southerners.
	\item This was an escape clause for wealthy planters which was used frequently.
\end{enumerate}

\subsubsection{Southern Governments of 1865}
\begin{enumerate}
	\item After 8 months, 11 of ex-Confederate states qualified under the Reconstruction plan to 
		become parts of the Union.
	\item None of the new constitutions extended voting rights to blacks. 
	\item Former leaders of the Confederacy won seats in Congress.
\end{enumerate}

\subsubsection{Black Codes}
\begin{enumerate}
	\item Southern state legislatures adopted Black Codes that restricted the rights and movements
		of the former slaves.
	\item Codes 
	\begin{enumerate}
		\item prohibited blacks from either renting land or borrowing money to buy land
		\item placed freedmen into a form of semibondage by forcing, as "vagrants" and "apprentices"
			to sign work contracts
		\item prohibited blacks from testify against whites in court.
	\end{enumerate}
	\item The contract-labor system seemed little different from slavery.
	\item Northern Republicans in Congress refused to seat duly elected representatives and senators
		from ex-Confederate states.
\end{enumerate}

\subsubsection{Johnson's Vetoes}
\begin{enumerate}
	\item Johnson vetoed a bill increasing the services and protection offered by Freedmen's Bureau
	\item He also vetoed a bill that nullified the Black Codes and guaranteed full citizenship to 
		African Americans
	\item This alienated even moderate Republicans 
\end{enumerate}

\section{Congressional Reconstruction}
\begin{enumerate}
	\item Angry response by members of Congress led to the second round of Reconstruction.
	\item Featured policies that were
	\begin{enumerate}
		\item hasher on Southern whites
		\item more protective of freed African Americans
	\end{enumerate}
\end{enumerate}

\subsection{Radical Republicans}
\begin{enumerate}
	\item Republicans were divided between
	\begin{enumerate}
		\item moderates (were chiefly concerned with economic gains for white middle class)
		\item radicals (championed civil rights for blacks)
	\end{enumerate}
	\item More Republicans became radical in fear that the Democratic party might become dominant
		again
	\item Since the federal census counted all people equally, the South would have more 
		representatives in Congress
	\item Charles Sumner of Massachusetts was the leading Radical Republican (who got cane by Brooks)
	\item Radical Republicans endorsed several liberal causes including
	\begin{enumerate}
		\item women's suffrage
		\item rights for labor unions
		\item civil rights for Northern African Americans
	\end{enumerate}
\end{enumerate}

%\subsubsection{Civil Rights Act of 1866}
%\begin{enumerate}
%	\item First, 
%\end{enumerate}

\end{document}
